---
title: "QF 202 Quiz 9"
date: "4/7/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(quantmod)
library(runner)
```

# Question 1

Download stock price data for Apple (AAPL) from 2021-01-01 to 2021-12-31 and calculate log return sequence using `dailyReturn` function .

```{r}
getSymbols('AAPL', from = "2021-01-01", to = "2021-12-31", src = "yahoo")
head(AAPL)
```
```{r}
AAPL_log_returns <- dailyReturn(AAPL, type = "log")
head(AAPL_log_returns)
```

# Question 2

Using expanding window to calculate the average of log return of AAPL.
```{r}
average_expanding_window <- runner(
  AAPL_log_returns$daily.returns,
  f = mean
)
AAPL_log_returns <- cbind(AAPL_log_returns, average_expanding_window)
head(AAPL_log_returns)
```


# Question 3

Using rolling window to calculate the average of log return of AAPL with window size = 6

```{r}
average_rolling_window6 <- runner(
  AAPL_log_returns$daily.returns,
  k = 6,
  f = mean
)
AAPL_log_returns <- cbind(AAPL_log_returns, average_rolling_window6)
head(AAPL_log_returns,20)
```

# Do not forget to compile the source file to a report before you submit it on Canvas!
