---
title: "QF 202 Quiz 11"
date: "4/14/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load libraries
library(quantmod)
library(forecast)
```

# Question 1

Download stock price data for AAPL (AAPL) from 2021-01-01 to 2021-12-31 and calculate log return sequence using `dailyReturn` function .

```{r}
getSymbols('AAPL', from = "2021-01-01", to = "2021-12-31", src = "yahoo")
head(AAPL)
```
```{r}
ret <- dailyReturn(AAPL, type = "log")
head(ret)
```


# 2. Use brute force method to select the best fitted ARMA model
```{r}
# define max order
ma.order.vec <- seq(1, 3)
ar.order.vec <- seq(1, 3)

arma.order.list <- expand.grid(p = ar.order.vec, d=0, q=ma.order.vec)
arma.order.list <- rbind(c(0,0,0), arma.order.list)
arma.order.list <- as.data.frame(t(arma.order.list))
arma.order.list <- as.list(arma.order.list)

# define aic function
get.arma.aic <- function(order) arima(ret,order=order)$aic

# calculate aic
arma.aic.vec <- sapply(arma.order.list, get.arma.aic)

# show the best ARMA
selected_order <- arma.order.list[[which.min(arma.aic.vec)]]
selected_order

best_model <- arima(ret, order = selected_order)
best_model
```

```{r}
# or
forecast::auto.arima(ret, d=0, max.p = 5, max.q = 5, trace=FALSE, ic = c("aic"))
```


# 3. Using the models you evaluated in problem 2, please forecast the return for: 5 days. Write down the expected return of the 5th day. 

```{r}
forecast(ret, model=best_model, h=5)
```
*The expected return of the 5th day is 0.001525*

# Do not forget to compile the source file to a report before you submit it on Canvas!
