---
title: "QF 202 Quiz 8"
date: "3/9/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(2022)

library(forecast)
```

# Question 1

1. Please analyze the following code. Run the code to generate a sequence of length = 10000. 

```{r}
n = 10000
a<-rnorm(n)
r<-vector(length=n)
r[1]=r[2]=0
for (t in 3:n) {
  r[t] = 0.5*r[t-1]+0.4*r[t-2]+a[t]
}
```

Please write down in the provided space the name of the model, its formula dynamics using the numerical values of the parameters.

The model is ar2 model, and its formula dynamics prints out an accurate estimation of the distribution of those models. This is based on the n number of points within the distribution.



2. Fit the data to the model using `arima()` function, and the proper order. Display the results from `tsdiag()` and state your observations.
```{r}
model_5000.ar2 <- arima(r, order=c(2,0,0), include.mean = F)

 
tsdiag(model_5000.ar2)
```

3. Output 5-step prediction using the estimated model. 

```{r}
predict(r,5)
```


# Do not forget to compile the source file to a report before you submit it on Canvas!
