---
title: "HW3 - Introduction to Financial Time Series"
author: "Brennan Hall"
date: "03/20/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("forecast")
```

# Problem 1

Please download the attached data (T-notes.csv).

```{r}
# Load the Data
t.notes <- read.csv("T-notes.csv",header=T, row.names = 1)

# Put in the right order
t.notes <- t.notes[nrow(t.notes):1,]

```
## (a) Simple return and Split the data

```{r}
# Calculate the daily simple return
t.notes.ret <- diff(t.notes)/ t.notes[-length(t.notes)]

# Split the result into two separate subsets.
# The first one (DATA 1) contains the first 200 daily returns.
n <- length(t.notes.ret)
data1 <- t.notes.ret[1:200]

# The second subset (DATA 2) contains the remaining daily returns
data2 <- t.notes.ret[201:n]
```

## (b) ACF
```{r}
# Create an ACF plot usinf the T-notes return in DATA 1
acf(data1, lag.max = 20)
# Report the values of the first 20 lags of autocorrelation.
acf(data1, lag.max = 20, plot = FALSE)
```

## (c) PACF
```{r}
# Use the PACF function to plot the partial autocorrelations using DATA 1. 
pacf(data1)

# Based on the plots what is the recommended order p if we want to fit an AR(p)
# model on DATA 1.

# AR(1) or AR(4) could be good.
```

## (d) Fit mode1 using the ARIMA function
```{r}
# Use the ARIMA function and the order p you determined in previous problem fit
# an AR(p) model on DATA 1. Name this fitted model as MODEL 1.

# AR(1)
model1 <- arima(data1, order=c(1,0,0), include.mean = F)
model1
```

## (e) Fit model2 using ar() function
```{r}
# Use the builtin function ar() and your preferred criteria to fit another AR
# model on DATA 1. Name this fitted model as MODEL 2.
model2 <- ar(data1, aic = TRUE)
model2
```

## (f) Predict the daily returns for the next 20 days
```{r}
# For each model, predict the daily returns for the next 20 days.
predict(model1, n.ahead = 20)
predict(model2, n.ahead = 20)
# forecast(model1, 20, level = c(90, 95))
# forecast(model2, 20, level = c(90, 95))

# Plot MODEL 1 predicted values following the original values in DATA 1.
plot(forecast(model1, n.ahead = 20), xlim =c(150, 210))

# Plot MODEL 2 predicted values following the original values in DATA 1.
plot(forecast(model2, n.ahead = 20), xlim =c(150, 210))
```

## (g) MSE
```{r}
# Using DATA 2, compute the mean squared error (MSE) for each AR model you constructed.

# h.ahead <- length(data2)
h.ahead <- 20

model1.pred <- predict(model1, n.ahead = h.ahead)$pred
model2.pred <- predict(model2, n.ahead = h.ahead)$pred

model1.mse <- mean((as.vector(model1.pred) - data2[1:h.ahead])^2)
model2.mse <- mean((as.vector(model2.pred) - data2[1:h.ahead])^2)

# Compare the MSE values for the models.
model1.mse
model2.mse

# It seems that the model 1 is better, since has smaller MSE.
```

# Problem 2

## (a) Calculate the theoretical autocorrelation values for these models.

```{r}
# MA(1) using the given formula
.7 / (1+.7^2)

# Using ARMAacf function
ARMAacf(ma=0.7)[2]

# # Plot the theoretical autocorrelation value
# barplot(ARMAacf(ma=0.7,lag.max=12)[-1],main = "ACF of ma(1)")
```

```{r}
# MA(2) using the given formula
(.5 + .5*.3)/(1+.5^2+.3^2) # p1
(.3)/(1+.5^2+.3^2) # p2

# Using ARMAacf function
ARMAacf(ma=c(0.5,0.3))[2:3]

# # Plot the theoretical autocorrelation value
# barplot(ARMAacf(ma=c(0.5,0.3),lag.max=12)[-1],main = "ACF of ma(2)")
```

## (b) Using arima.sim() function to generate 5000 data points of corresponding MA(1) model and
calculate the ACF value for this data set.
```{r}
data_generate1 <- arima.sim(list(ma =0.7), n = 5000)
s1 <- acf(data_generate1, lag=15) # Obtain the ACF plot and more.
s1$acf[-1]
```
## (c) Using arima.sim() function to generate 5000 data points of corresponding MA(2) model and
calculate the ACF value for this data set.
```{r}
data_generate2 <- arima.sim(list(ma =c(0.5, 0.3)), n = 5000)
s2 <- acf(data_generate2, lag=15) # Obtain the ACF plot and more.
s2$acf[-1]
```

## (d) Present a table with the theoretical values and estimated values. Comment on what you observe.
```{r}
data.frame(
  Theoretical_MA1=ARMAacf(ma=0.7, lag.max = 10)[-1],
  Estimated_MA1=s1$acf[2:11],
  Theoretical_MA2=ARMAacf(ma=c(0.5,0.3), lag.max = 10)[-1],
  Estimated_MA2=s2$acf[2:11]
)
# We can see that the estimated values is very near the theoretical values.
```
# BONUS

The values above are for n = 5000. Repeat the procedure for a series of n values and study
the differences between the real and estimated values as a function of n. In your opinion what
is the order of this function. That is, how does this difference goes to 0 as n goes to infinite

```{r}
n_sim = 50
data_generate1 <- arima.sim(list(ma =0.7), n = n_sim)
s1 <- acf(data_generate1, lag=15, plot = FALSE) # Obtain the ACF plot and more.
data_generate2 <- arima.sim(list(ma =c(0.5, 0.3)), n = n_sim)
s2 <- acf(data_generate2, lag=15, plot = FALSE) # Obtain the ACF plot and more.
data.frame(
  Theoretical_MA1=ARMAacf(ma=0.7, lag.max = 10)[-1],
  Estimated_MA1=s1$acf[2:11],
  Theoretical_MA2=ARMAacf(ma=c(0.5,0.3), lag.max = 10)[-1],
  Estimated_MA2=s2$acf[2:11]
)

n_sim = 500
data_generate1 <- arima.sim(list(ma =0.7), n = n_sim)
s1 <- acf(data_generate1, lag=15, plot = FALSE) # Obtain the ACF plot and more.
data_generate2 <- arima.sim(list(ma =c(0.5, 0.3)), n = n_sim)
s2 <- acf(data_generate2, lag=15, plot = FALSE) # Obtain the ACF plot and more.
data.frame(
  Theoretical_MA1=ARMAacf(ma=0.7, lag.max = 10)[-1],
  Estimated_MA1=s1$acf[2:11],
  Theoretical_MA2=ARMAacf(ma=c(0.5,0.3), lag.max = 10)[-1],
  Estimated_MA2=s2$acf[2:11]
)

n_sim = 1000
data_generate1 <- arima.sim(list(ma =0.7), n = n_sim)
s1 <- acf(data_generate1, lag=15, plot = FALSE) # Obtain the ACF plot and more.
data_generate2 <- arima.sim(list(ma =c(0.5, 0.3)), n = n_sim)
s2 <- acf(data_generate2, lag=15, plot = FALSE) # Obtain the ACF plot and more.
data.frame(
  Theoretical_MA1=ARMAacf(ma=0.7, lag.max = 10)[-1],
  Estimated_MA1=s1$acf[2:11],
  Theoretical_MA2=ARMAacf(ma=c(0.5,0.3), lag.max = 10)[-1],
  Estimated_MA2=s2$acf[2:11]
)

# As n goes from 0 to infinite we can see that the estimated values is more
# closer to the theoretical values.
```



